DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
Cleaning Perceived Opportunities Data Set

# Import fear of failure data
FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)

# Import current owner data
CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)

# Import entrepreneurial intention data
EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)

# Import nascent entrepreneur data
NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)

# Import perceived capabilities data
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)

@@

>>>>

# Import GEM fear of failure data
FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)

# Import GEM estblished entrepreneurship - current owner data
CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)

# Import GEM entrepreneurial intention data
EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)

# Import GEM nascent entrepreneur data
NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)

# Import GEM perceived capabilities data
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)

# Import GEM perceived opportunities data as a proxy for potential control variables
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedOpportunities.csv", header = TRUE, cache = FALSE)

@@

### Clean PerceivedOpportunities ###
# Percentage of 18-64 population who see good opportunities to start a firm in the area where they live

# Remove X's in PerceivedOpportunities year columns
names(PerceivedOpportunities) <- gsub("X", "", names(PerceivedOpportunities))

# Change years from columns to rows and create CPreceivedCapabilities
CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentOpportunities"))
